Diversity

### 2020-01-22 manuscript/supp/code/18s_asv_clust.Rmd

```{r, include=F}
library(tidyverse)
library(DECIPHER)
library(ape)
library(ggtree)
```

@@

```{r, include=F}
BrowseSeqs(aligns, highlight = T)

@@

mds <- ggplot(mds_coords_w_taxonomy, aes(x=V1, y=V2))+
  geom_point(aes(color=best_assignment, size=rel_abund), alpha=0.7, na.rm=TRUE) +
  scale_color_manual(values= colors) +
  guides(size="none",
         colour = guide_legend(override.aes = list(size=5, alpha=1))) +
  # include pts not assigned taxonomy
  geom_point(data = filter(mds_coords_w_taxonomy, is.na(best_assignment)), 
             color = "grey", alpha = 0.8) +
  labs(color="Taxonomic assignment")
mds
```

@@

tsne <- ggplot(tsne_pts_taxonomy, aes(x=V1, y=V2)) +
  geom_point(data = tsne_pts_taxonomy, 
             aes(color = best_assignment, size=rel_abund), 
             alpha = 0.8, na.rm=TRUE) +
  # include points not assigned to genus or species
  geom_point(data = filter(tsne_pts_taxonomy, is.na(best_assignment)), 
             color = "grey", alpha = 0.8) +
  scale_color_manual(values= colors) +
  guides(size="none",
         colour = guide_legend(override.aes = list(size=5, alpha=1))) +
  labs(color="Taxonomic assignment")

tsne

@@

Perplexity = 20.

\pagebreak

# Maximum likelihood tree (IQTree)

@@

tree_out <- ggtree(tree) +
  geom_text2(data=boots, aes(label=paste0(boot,";",bayes)),  vjust= 0.01, hjust = 1, size=2) +
  geom_tippoint(data = annotate, aes(color= best_assignment, size=rel_abund), alpha=1, na.rm=TRUE) + 
  theme(legend.position = c(0.89,0.7),
        legend.title = element_blank(),
        legend.key = element_blank()) +
  scale_color_manual(values= colors) +
  geom_tiplab(data = annotate, aes(label = best_assignment), size=2)+
  guides(size="none")

tree_out
```

>>>>

```{r, include=F}
library(tidyverse)
library(DECIPHER)
library(ape)
library(ggtree)
library(gridExtra)
library(ggpubr)
library(cowplot)
```

@@

```{r, include=F}
# BrowseSeqs(aligns, highlight = T)

@@

mds_1 <- ggplot(mds_coords_w_taxonomy, aes(x=V1, y=V2))+
  geom_point(aes(color=best_assignment, size=rel_abund), alpha=0.7, na.rm=TRUE) +
  scale_color_manual(values= colors) +
  guides(size="none",
         colour = guide_legend(override.aes = list(size=5, alpha=1))) +
  # include pts not assigned taxonomy
  geom_point(data = filter(mds_coords_w_taxonomy, is.na(best_assignment)), 
             color = "grey", alpha = 0.8) +
  labs(color="Taxonomic assignment", tag="A")

legend <- mds_1 %>% 
  cowplot::get_legend() %>% 
  ggpubr::as_ggplot()

mds <- mds_1 +
  theme(legend.position = "none")

@@

tsne <- ggplot(tsne_pts_taxonomy, aes(x=V1, y=V2)) +
  geom_point(data = tsne_pts_taxonomy, 
             aes(color = best_assignment, size=rel_abund), 
             alpha = 0.8, na.rm=TRUE) +
  # include points not assigned to genus or species
  geom_point(data = filter(tsne_pts_taxonomy, is.na(best_assignment)), 
             color = "grey", alpha = 0.8) +
  scale_color_manual(values= colors) +
  guides(size="none",
         colour = guide_legend(override.aes = list(size=5, alpha=1))) +
  labs(color="Taxonomic assignment", tag="B") +
  theme(legend.position = "none")

@@

@@

tree_out <- ggtree(tree) +
  geom_text2(data=boots, aes(label=paste0(boot,";",bayes)),  vjust= 0.01, hjust = 1, size=2) +
  geom_tippoint(data = annotate, aes(color= best_assignment, size=rel_abund), alpha=1, na.rm=TRUE) + 
  theme(legend.position = c(0.89,0.7),
        legend.title = element_blank(),
        legend.key = element_blank()) +
  scale_color_manual(values= colors) +
  geom_tiplab(data = annotate, aes(label = best_assignment), size=2)+
  guides(size="none") +
  labs(tag="C") +
  theme(legend.position = "none")
```

```{r, fig.width=8, fig.height=10}
lay <- rbind(c(1,1,4),
             c(2,2,4),
             c(3,3,4),
             c(3,3,4),
             c(3,3,4))
gridExtra::grid.arrange(mds, tsne, tree_out, legend, layout_matrix=lay)

### 2020-01-22 manuscript/supp/code/diversity.Rmd

```{r, include=F}
rel_abund <- read_csv(here::here("data/rel_abund/3_filter/rbcl/rbcl_rel_abund.csv")) # not looking at the depth samples, controls, etc
tax <- read_csv(here::here("data/taxonomy/tidied.rbcl_taxonomy.csv"))
field <- read_csv(here::here("data/field/tidy_field.csv"))
asv_seqs <- read_csv(here::here("data/fastas/asv_seq_data/rbcl_asv_sequence_key.csv"))
otus <- read_csv(here::here("data/otus/otu_rbcl_asvs.csv"))
rbcl.tree <- read.tree(here::here("data/tree/rbcl/asv613.fasta.treefile")) ### this tree should only contain the asvs we found in the "main" sites, not looking at controls, etc
```

```{r, include=F}
# get relative abundance of each otu, in wide format, 
otu_rel_abund <- rel_abund %>% 
  left_join(otus, by="asv_id") %>% 
  group_by(sample_id, otu_name) %>% 
  summarise(rel_abund = sum(rel_abund)) %>%   
  ungroup() %>% 
  pivot_wider(names_from = otu_name, values_from = rel_abund, values_fill = list(rel_abund=0)) %>% 
  column_to_rownames("sample_id") # vegan::diversity() wants sample identifiers as rownames

@@

```{r, include=F}
# format
ra_wide <- rel_abund %>% 
  select(sample_id, asv_id, rel_abund) %>% 
  arrange(asv_id) %>% 
  pivot_wider(names_from = asv_id, values_from = rel_abund, values_fill = list(rel_abund = 0)) %>% 
  column_to_rownames("sample_id")

>>>>

```{r, include=F}
rbcl_rel_abund <- read_csv(here::here("data/rel_abund/3_filter/rbcl/rbcl_rel_abund.csv")) # not looking at the depth samples, controls, etc
tax <- read_csv(here::here("data/taxonomy/tidied.rbcl_taxonomy.csv"))
field <- read_csv(here::here("data/field/tidy_field.csv"))
asv_seqs <- read_csv(here::here("data/fastas/asv_seq_data/rbcl_asv_sequence_key.csv"))
otus <- read_csv(here::here("data/otus/otu_rbcl_asvs.csv"))
rbcl.tree <- read.tree(here::here("data/tree/rbcl/asv613.fasta.treefile")) ### this tree should only contain the asvs we found in the "main" sites, not looking at controls, etc
```

```{r, include=F}
# get relative abundance of each otu, in wide format, 
otu_rel_abund <- rbcl_rel_abund %>% 
  left_join(otus, by="asv_id") %>% 
  group_by(sample_id, otu_name) %>% 
  summarise(rel_abund = sum(rel_abund)) %>%   
  ungroup() %>% 
  pivot_wider(names_from = otu_name, values_from = rel_abund, values_fill = list(rel_abund=0)) %>% 
  column_to_rownames("sample_id") # vegan::diversity() wants sample identifiers as rownames

@@

```{r, include=F}
# format
ra_wide <- rbcl_rel_abund %>% 
  select(sample_id, asv_id, rel_abund) %>% 
  arrange(asv_id) %>% 
  pivot_wider(names_from = asv_id, values_from = rel_abund, values_fill = list(rel_abund = 0)) %>% 
  column_to_rownames("sample_id")
